---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# covidphdata: An Interface to the Philippines Department of Health COVID-19 Data Drop

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
![R-CMD-check](https://github.com/como-ph/covidphdata/workflows/R-CMD-check/badge.svg)
<!-- badges: end -->

The Philippines Department of Health has made COVID-19 related data publicly available as part of its mandate to promoting transparency and accountability in governance. The Philippines COVID-19 Data Drop is distributed via Google Drive with latest updated data provided daily. Data from previous days are archived and also made available through Google Drive. This package provides a coherent and performant API to the latest and archived Philippines COVID-19 data.

## Installation

<!---
You can install the released version of covidphdata from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("covidphdata")
```
--->

`covidphdata` is not yet available on [CRAN](https://cran.r-project.org).

The development version of `covidphdata` can be installed via GitHub:

```{r install, echo = TRUE, eval = FALSE}
if(!require(remotes)) install.packages("remotes")
remotes::install_github("como-ph/covidphdata")
```

## Usage


